Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-07 Documents/Paper/ms.tex
Acceptance rate

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space.

@@

Most of the proposals discussed in this paper involve changing one
(or a subset) of the parameters and/or hyperparameters, while keeping the
others fixed. Whenever a heavy-tailed proposal distribution
is required, we use the proposal from Equation~\ref{eqn:heavytailed},
or an analogous one, e.g. a discrete version when the proposal is to change $N$.

>>>>

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space.
A C++ implementation of DNS, called {\tt DNest3}, is available at
{https://github.com/eggplantbren/DNest3}.

@@

Most of the proposals discussed in this paper involve changing one
(or a subset) of the parameters and/or hyperparameters, while keeping the
others fixed. Whenever a heavy-tailed proposal distribution
is required, we use the proposal from Equation~\ref{eqn:heavytailed},
or an analogous one, e.g. a discrete version when the proposal is to change $N$.
The {\tt DNest3} package monitors the acceptance rate as a function of level.
In most applications, the acceptance probability is close to 1 (or may be
precisely 1) when sampling the prior, and decreases to 5-40\% when sampling
high levels.
